Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-08-15 paper/paper.tex
Another experiment we need
Move things around

\section{Some Maths}
A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping
$P \rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An induced subgraph
isomorphism $P \hookrightarrow T$, additionally maps non-adjacent vertices to non-adjacent
 vertices.

@@

@@

\todo{Define $\preceq$, deg, nds, paths}

@@

@@

@@

\section{An Algorithm}

@@

Comparison with the clique and CP models.

@@

Just results.

@@

\subsection{Filtering and Propagation}

\subsubsection{Initial Domain Sizes}

Remember loops can make this overly optimistic if we just take the products!

\subsubsection{Is Path Filtering Useful?}

>>>>

\subsection{Definitions and Notations}

A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping
$P \rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An induced subgraph
isomorphism $P \hookrightarrow T$, additionally maps non-adjacent vertices to non-adjacent
 vertices.

@@

\subsection{Models and Algorithms}

\section{Domain Filtering}

@@

\todo{Define $\preceq$, deg, nds}

@@

\section{Filtering During Search}

@@

\todo{Define paths}

@@

\section{A New Algorithm}

@@

Comparison with the clique and CP models, as well as ``drop k vertices and try each in turn''.

@@

Just results and ``drop k vertices and try each in turn''.

@@
